\begin{resume}

\begin{resumesection}{Brief biography}


\end{resumesection}

\begin{publicationlist}{Journal Publications}{9}
    \item 第一作者.  An Automated Weld Seam Tracking System for Thick Plate Welding Robots Using Cross-mark Structured Light.
        \emph{International Journal of Advanced Manufacturing Technology}, Vol.89 (9), pages 3589-3603, 2016. \textbf{(SCI indexed)}

    \item 第一作者.  A Practical and Intuitive Calibration Technique for Cross-line Structured Light.
        \emph{International Journal for Light and Electron Optics}, Vol.127 (20), pages 9582-9602, 2016. \textbf{(SCI indexed)}

    \item 第一作者. A Real-time and Robust Feature Detection Method Using Hierarchical Strategy and Modified Kalman Filter for Thick Plate Seam Tracking.
        \emph{International Journal of Automation and Control}, published on-line, 2017. \textbf{(EI indexed)}

\end{publicationlist}

\begin{publicationlist}{Conference Publications}{9}
    \item 第一作者. A Geometry Based Feature Detection Method of V-Groove Weld Seam for Thick Plate Welding Robots.
        \emph{IEEE International Conference on Control and Robotics Engineering}, pages 43-48, 2017. \textbf{(EI indexed)}

    \item 第一作者.  A Simple Technique for Structured Light Calibration in Welding Robots.
        \emph{IEEE International Conference on Robotic and Biomimetics}, pages 596-601, 2015. \textbf{(EI indexed)}

    \item 第一作者. Visual Recognition of the Initial and End Points of Lap Joint for Welding Robots.
        \emph{IEEE International Conference on Information and Automation}, pages 513-518, 2014. \textbf{(EI indexed)}

\end{publicationlist}

\begin{publicationlist}{Under reviewed papers}{9}
    \item 第一作者. A Real-Time Tracking Control for Thick Plate Weld Seam Robots Based on Bayesian Filters.
        \emph{Journal of Intelligent \& Robotics Systems}. \textbf{(SCI indexed)}

    \item 第一作者. RANSAC Algorithm Based Calibration Method for Active Visual Sensing Systems.
        \emph{Machine Vision and Applications}. \textbf{(SCI indexed)}

\end{publicationlist}

\begin{publicationlist}{Awards}{9}
    \item 2014 Best Paper Final List of IEEE International Conference on Information and Automation
    \item 2016 Excellent International Students of University of Chinese Academy of Sciences(UCAS)

\end{publicationlist}

\begin{publicationlist}{Contributions}{9}
    \item A reviewer of Optics and Lasers in Engineering(SCI indexed journal)

\end{publicationlist}

\end{resume} 